An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-03-23 uai2017/paper.tex
update paper and results

Figure~\ref{fig:gauss_mix_2} shows that {\sc MHminibatch} dominates in terms of
speed and efficiency. The histograms of the (final) minibatch sizes used each
iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 213, more than an order of
magnitude better compared to the other two methods (averages are 11962 and
63408). Sizes correspond to the running times of the methods, excluding the
likelihood computation of all data points for {\sc MHSubLhd}, which would
drastically increase running time.

>>>>

Figure~\ref{fig:gauss_mix_2} shows that {\sc MHminibatch} dominates in terms of
speed and efficiency. The histograms of the (final) minibatch sizes used each
iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 172, more than an order of
magnitude better compared to the other two methods (averages are 12562 and
675008). We further ran 10 runs of mixture of Gaussians experiments, and
the average and standard deviation values of the mean minibatch size 
for {\sc MHminibatch}, {\sc AustereMH(c)}, {\sc MHSubLhd} are listed in
table ~\ref{tab:gaussianres}. Sizes correspond to the running times of the methods, excluding the
likelihood computation of all data points for {\sc MHSubLhd}, which would
drastically increase running time.

\begin{table}[t]
\caption{Statistics for mean minibatch sizes on gaussian mixture model
experiments using {\sc MHminibatch}, {\sc AustereMH(c)}, {\sc MHSubLhd}.
The averages are taken over 10 independent trials (3000 samples each).}
\small % Daniel: yeah, sorry, but otherwise it doesn't fit in a column
\label{tab:gaussianres}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Method/Data} & \textbf{Average of Mean} & \textbf{Std of Mean}  \\
\hline \\
{\sc MHminibatch}   & 182 & 12 \\
{\sc AustereMH(c)}  & 13540 & 1521 \\
{\sc MHSubLhd}      & 65759 & 3222 \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}
